Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-23 paper/paper.qmd
update paper

To further explore the contextual relationship between each word, @fig-word-networks creates word networks of all nine of these SOC texts. These networks will capture how often each word frequents in these SOC texts and how closely each correlates with others, whether as single words (unigrams) or pairs of words (bigrams). In particular, the darker the connecting lines, the more correlative these combinations of words are, and the bluer the words, the more frequent they appear. When combined all SOC texts, similarly, temporal nouns like \textit{time, day, life, moment, night} appear the most, at, respectively, 870, 597, 567, 502 and 376 times. This further correlates to the non-linear nature of SOC literature and their exploration of cognitive incoherence. In terms of correlation, forgoing personal names like \textit{swann, odette or mme}, bigrams with a correlation of 1 include those like \textit{dark, love}; \textit{day, heart}; \textit{moment, life}; \textit{mind, life}; \textit{moment, mind}, among others. Observable from  @fig-word-networks, with a correlation and a word count of at least 0.8 and 400, \textit{people, moment, life} and \textit{mind} are the most predominant word combinations throughout all 9 SOC texts.

>>>>

To further explore the contextual relationship between each word, @fig-word-networks creates word networks of all nine of these SOC texts. These networks will capture how often each word frequents in these SOC texts and how closely each correlates with others, whether as single words (unigrams) or pairs of words (bigrams). When combined all SOC texts, temporal nouns like \textit{time, day, life, moment, night} appear the most, at, respectively, 870, 597, 567, 502 and 376 times. This further correlates to the non-linear nature of SOC literature and their exploration of cognitive incoherence. In terms of correlation, forgoing personal names like \textit{swann, odette or mme}, bigrams with a correlation of 1 include those like \textit{dark, love}; \textit{day, heart}; \textit{moment, life}; \textit{mind, life}; \textit{moment, mind}, among others. Observable from  @fig-word-networks, with a correlation and a word count of at least 0.8 and 400, \textit{people, moment, life} and \textit{mind} are the most predominant word combinations throughout all 9 SOC texts.
